### 2021-04-04 Chapter-3/Chapter-3.tex
update

                                               &                        &                     &                      &              & ms                     \\\cline{7-7}

@@

      AES&   OpenSSL 1.0.2k       & 88         & 0                   & 88                   & 1,350        & 35   \\

@@

                         &                        &                     &                      &                 & minutes            \\\cline{7-7}
      RSA &    mbedTLS 2.5   & 6            & 6          & 0                    & 22,109,246    & 39      \\
      RSA &    mbedTLS 2.15    & 12          & 12     & 0                    & 24,484,441    & 44        \\
      RSA &     OpenSSL 0.9.7      & 107     & 105           & 2                    & 17,002,523   & 23  \\
      RSA &    OpenSSL 1.0.2f      & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
      RSA &   OpenSSL 1.0.2k      & 36              & 27                  & 9                    & 15,285,210   & 40      \\
      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
      RSA & & 11& 9& 2& 9,527,231& 2 \\
      RSA & & 14& 14& 0& 10,513,606& 14  \\
      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\

      Total              & 904                    & 241                 & 663                & 167,141,947      & 341m  \\\hline
  \end{tabular}
\end{table*}

>>>>

                       &                          &                   &                &                &             & ms      \\\cline{7-7}

@@

    AES                & OpenSSL 1.0.2k           & 88                & 0              & 88             & 1,350       & 35      \\

@@

                       &                          &                   &                &                &             & minutes \\\cline{7-7}
    RSA                & mbedTLS 2.5              & 6                 & 6              & 0              & 22,109,246  & 39      \\
    RSA                & mbedTLS 2.15             & 12                & 12             & 0              & 24,484,441  & 44      \\
    RSA                & OpenSSL 0.9.7            & 107               & 105            & 2              & 17,002,523  & 23      \\
    RSA                & OpenSSL 1.0.2f           & 38                & 27             & 11             & 14,468,307  & 29      \\
    RSA                & OpenSSL 1.0.2k           & 36                & 27             & 9              & 15,285,210  & 40      \\
    RSA                & OpenSSL 1.1.0f           & 31                & 22             & 9              & 16,390,750  & 34      \\
    RSA                & OpenSSL 1.1.1            & 4                 & 4              & 0              & 18,207,016  & 8       \\
    RSA                & OpenSSL 1.1.1g           & 8                 & 8              & 0              & 18,536,796  & 5       \\
    RSA                & Libgcrypt 1.6.1          & 11                & 9              & 2              & 9,527,231   & 2       \\
    RSA                & Libgcrypt 1.7.3          & 14                & 14             & 0              & 10,513,606  & 14      \\
    RSA                & Libgcrypt 1.8.5          & 8                 & 8              & 0              & 27,407,986  & 113     \\

    Total              &                          & 904               & 241            & 663            & 167,141,947 & 341m    \\\hline
  \end{tabular}
\end{table*}
